Fractional Types

### 2019-11-07 fracGC/p.tex
using new trick to typeset code; seems to work fine

\usepackage{booktabs}  
\usepackage{subcaption}

@@

@@

X -> X * Y * 1/Y 
  -> A * 1/Y
  -> B * 1/Y
  -> Y * Z * 1/Y
  -> Z * Y * 1/Y
  -> Z
\end{verbatim}
This basically says, in the language of Lens, that
when $A$ is isomorphic to $X \cross Y$ and
$B$ is isomorphic to $Z \cross Y$, then
$X$ is isomorphic to $Y$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pi}

Adding variables to Pi first?

@@

Add eta/epsilon leading to \verb|C3.agda|. This code has a runtime
check like current solutions but is more general allowing non-scoped
ancilla allocation and de-allocation. Show examples.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comonad}

Comonad to keep track to value in focus

Now we define pointed types $\pointed{t}{v}$ which are a record
consisting of a value type together with a value of that type. Both
the level-1 and level-2 program lift naturally to the world of pointed
types but instead of manually rewriting everything we use the fact
that pointed types form a comonad. So for example, given a level-1
program we should be able to just use \textsf{extend} to compose
instead of plain composition of combinators??

Then we can define $\eta$ and $\epsilon$ in the comonadic world.

Exploit dependent types to reify proofs in the type system. Type
checking requires (partial) eval. Once we have a proof can we somehow
go back to \verb|C3.agda| and remove the runtime check?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{../cites.bib}

>>>>

\usepackage{booktabs}  
\usepackage{subcaption} 
\usepackage{amssymb}
\usepackage{bbm}
\usepackage[greek,english]{babel}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{autofe}
\usepackage[references]{agda} 
\usepackage{newunicodechar}

\newunicodechar{𝕌}{$\mathbb{U}$}
\newunicodechar{𝟙}{$1$}
\newunicodechar{ᵤ}{${}_u$}

@@

\input{latex/PiFracDynCode.tex}

@@

X -> X * Y * 1/Y 
  -> A * 1/Y
  -> B * 1/Y
  -> Y * Z * 1/Y
  -> Z * Y * 1/Y
  -> Z
\end{verbatim}
This basically says, in the language of Lens, that
when $A$ is isomorphic to $X \times Y$ and
$B$ is isomorphic to $Z \times Y$, then
$X$ is isomorphic to $Y$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PiFrac}

%%%%%
\subsection{Pi}

@@

%%%%%
\subsection{Adding Fractions}

%%%%%
\subsection{Ancilla}

When ancilla bits are created they are created with a specific
value. This value is encoded in the circuit. We use a Singleton type
to remember this information. We add the following:

ETA SIG

The value of fractional type represents the ``garbage collector.''
The garbage collector is specialized to collect a single value, which
is the value used to create the ancilla value. At this point, if the
garbage collector encounters a different value, it doesn't know what
to do, and would need to throw an exception. This situation in
\verb|PiFracDyn.agda| is similar to current solutions (e.g. Quipper)
but actually more general as it allows non-scoped ancilla allocation
and de-allocation. Show examples.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Generalizing to Non-Scoped Ancilla}

Def. of universe is:

\Udef{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Dependently-Typed Garbage Collectors}

%%%%%
\subsection{Singleton Types}

Consider the type $\Sigma \mathbb{N} (\lambda n. n \equiv 5)$. Values
of that type are a number $m$ and a proof that this is number is equal
to 5. So we can have $(4 + 1, \textit{refl})$, $(2 + 3 ,
\textit{refl})$, and so on. All these syntactically different values
are identical to 5 and hence we can \emph{contract} the type to a
single point at 5.

The denotation of the fractional type is now:

RECIP

Exploit dependent types to reify proofs in the type system. Type
checking requires (partial) eval. Once we have a proof can we somehow
go back to \verb|PiFracDyn.agda| and remove the runtime check?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{../../cites.bib}
